Adopting agile in the large: motivations, success factors and challenges

### 2014-01-12 journal/article.tex
Notes, small corrections

\item
RQ1: Why are transformations initiated?

\item
RQ2: How do transformations usually proceed; do transformations exhibit patterns?

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara). The selected primary studies were coded
for data extraction and analysis. The entire process was audited by a third
external researcher (Lassenius).

@@

@@

From these searches we compiled a list of 117 possibly relevant papers that
should be matched by the keyword searches. The keyword search came to include 75
of the preliminarily selected papers. The missed 32 preliminary papers were
separately examined for inclusion, resulting in including 3 additional papers as
primary studies.

@@

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result 45 papers were selected for full text analysis. In
addition 2 papers were included from the references of the evaluated papers, and
3 papers were included from the results of the preliminary search. Finally, 50
papers were selected as primary studies.

>>>>

\item
RQ1: Why do large organizations initiate an agile transformation?

\item
RQ2: How do large scale agile transformations usually proceed; do
     transformations exhibit patterns?

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. The selection
of primary studies was done as a keyword based database search and manual
filtering of included studies. The filtering process was executed independently
by two researchers (Dikert, Paasivaara). The selected primary studies were coded
for data extraction and analysis. The entire process was audited by a third
researcher (Lassenius).

@@

% --> Why are the preliminary searches done?

@@

From these searches we compiled a list of 117 possibly relevant papers that
should be matched by the keyword searches. The keyword search came to include 75
of the preliminarily selected papers. The missed 32 preliminary papers were
separately examined for inclusion, resulting in including 3 additional papers as
primary studies.
% -->  Move this later.

@@

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result of the full text filtering 45 papers were selected
to be included.
In addition 2 papers were included from the references of the evaluated papers,
and 3 papers were included from the results of the preliminary search. Finally,
50 papers were selected as primary studies.
